---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "./man/figures/",
   eval = FALSE,
  comment = "#>"
)

library(MetaMaster)
Sys.setenv(R_CONFIG_ACTIVE = "default")
```

The goal of the MetaMaster package is to create meta data for LimeSurvey which are reproducible, tested, and in consequence error-free. The package provides functions to get the names of the master templates, the data of the master template, and to create new surveys based on a template.



## Preparation steps

In order to use the package, you may wish to adjust the parameters for the LimeSurvey API (user name, LimeSurvey instance, etc.). All parameters that are necessary to retrieve data from a test or production LimeSurvey instance are saved in the `config.yml` file. The next console shows the default parameters for the test instance.

``` yaml
default:
  tmp.server: "semiotikon"
  api_url: "http://www.semiotikon.de/lime2/index.php/admin/remotecontrol"
  tmp.user: "limeremote"
  tmp.credential: "IWBD3SnMfxcu"
```

To use the production parameters (OES server), set the `R_CONFIG_ACTIVE` to `production`.

```{r, eval=FALSE}
Sys.setenv(R_CONFIG_ACTIVE = "test")
```

## Meta Master in Action

The `Limer_GetMaster()` function returns the name of master template. If the parameter `template` is missing, the function returns the all master templates.

```{r, eval=FALSE}
#Load the package
library(MetaMaster)

#Get master template for all school types
#mastertemplatesdf <- get_MasterTemplate()
mastertemplatesdf <- Limer_GetMasterTemplate(template = FALSE)
head(mastertemplatesdf)
```

The latter is used to retrieve the meta data for all master templates: The `get_MasterMeta()` function returns the metadata for a specific master template. As the next console underlines, it needs a `surveyID` and `name` of the survey. The function returns variable names and text from the LimeSurvey API.

```{r, eval=FALSE}
#Get metadata for a specific master template
get_MasterMeta(id = "197865",
               name = "master_01_bfr_allg_gm_elt_00_2022_v4")
```

The `get_AllMasterMeta()` is a wrapper function for `get_MasterMeta` that returns the metadata for all master templates in LimeSurvey. With the parameter `export = TRUE` the function exports the data as an Excel file.

```{r, eval = FALSE}
#Get metadata for all master templates
#get_AllMasterMeta(export = TRUE)
```

This file is used to create the meta data for all master templates. 







If a report template contains variables names that cannot be matched with the manual meta data, the function only appends variables names from LimeSurvey that cannot be matched. Thus, the result from `create_metadata` shows templates without errors (all columns are filled) and templates with errors (only variables names and text are listed). For example, the last console showed that the template `rpt_elt_p1` contains errors. The file shows which variables cannot be matched.













## Sent via API

Finally, the package provides a function to create a new survey based on a master template. The `send_survey()` function needs the path to the master template and the name of the new survey.

```{r, eval=FALSE}
#Create a new survey
Limer_sendSurvey(lss = "struktur_LimeSurvey.lss",
                 name = "SurveyName")
```

## Further Helpers

... 


