---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "./man/figures/",
   eval = FALSE,
  comment = "#>"
)

library(MetaMaster)
Sys.setenv(R_CONFIG_ACTIVE = "default")
```

The goal of the MetaMaster package is to create meta data for LimeSurvey which are reproducible, tested, and in consequence error-free. The package provides functions to get the names of the master templates, the data of the master template, and to create new surveys based on a template.



## Preparation steps





## Meta Master in Action



















## Sent via API

Finally, the package provides a function to create a new survey based on a master template. The `send_survey()` function needs the path to the master template and the name of the new survey.

```{r, eval=FALSE}
#Create a new survey
Limer_sendSurvey(lss = "struktur_LimeSurvey.lss",
                 name = "SurveyName")
```

## Further Helpers

... 


